---
title: "Evaluations of positive and negative stimuli using the Affective Misattribution Procedure (AMP) and self-reports"
subtitle: "Data processing"
author: "Template: Ian Hussey; content: [Viviane Widmer]"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    code_folding: hide
    highlight: haddock
    theme: flatly
    toc: yes
    toc_float: yes
---

```{r, include=FALSE}

knitr::opts_chunk$set(message = FALSE,
                      warning = FALSE)

```

# Dependencies

```{r}

library(dplyr)
library(tidyr)
library(readr)
library(janitor) # for clean_names()
library(stringr)

```

# Get data

```{r}

# demographics
data_demographics_raw_messy <- read_csv("../dat %>% a/raw/data_demographics_raw_messy.csv", skip = 2) |>
  janitor::clean_names()

data_demographics_raw <- read_csv("../data/raw/data_demographics_raw.csv") |>
  janitor::clean_names()

# self report measure
data_selfreport_raw <- read_csv("../data/raw/data_selfreport_raw.csv") |>
  janitor::clean_names()

# affect attribution procedure
data_amp_raw <- read_csv("../data/raw/data_amp_raw.csv") |>
  janitor::clean_names()

```

# Demographics

Clean the demographics data so that summaries of age and gender can be made in the analysis.

```{r}

#dat_age_gender <- data_demographics_raw 

#dat_age_gender <- data_demographics_raw %>%
 # rename(unique_id = subject, item = trialcode) %>%
  #select(unique_id, item, response)

#temp <- dat_age_gender %>%
#  filter(item == "age")

# wrangle the demographics data out of the raw
dat_age_gender <- data_demographics_raw %>%
  # rename for clarity
  rename(unique_id = subject, item = trialcode) %>%
  # select useful columns
  select(unique_id, item, response) %>%
  # retain raws that we need
  filter(item == "age")

#run the code again to check if it runs 
#look at the data to see if it's the way i like it to be

temp <- dat_age_gender %>%
  distinct(response)

#temp2 <- dat_age_gender %>% 
  #mutate allows you to change or create variables
 # mutate(unique_id_2 = unique_id * 2)
#we want to change response 

#went and asked chat gpt
temp2 <- dat_age_gender %>%
 # mutate(response = str_replace_all(response, " [^[:alnum:]]"))
  #because we want to remove all non numeric characters instead of replace: 
  mutate(response = str_remove_all(response, "\\D"),
         response = na_if(response, ""))


#homework for 7.10.24: do the same for gender! (Think of what could go wrong)
#to add # to multiple lines: Ctrl + shift + C

#temp <- dat_age_gender %>%
#  filter(item == "gender")

# wrangle the demographics data out of the raw
dat_age_gender <- data_demographics_raw %>%
  # rename for clarity
  rename(unique_id = subject, item = trialcode) %>%
  # select useful columns
  select(unique_id, item, response) %>%
  # retain raws that we need
  filter(item == "gender")

#run the code again to check if it runs 
#look at the data to see if it's the way i like it to be

temp2 <- dat_age_gender %>%
  distinct(response)

#wieso zeigt es mir nur 11 Zeilen an??

#possible issues: 
# The answers are in character, so everyone wrote the answer differently. All caps, no caps, somebody wrote 23?, Someone wrote yes. OVer all the data is not ready to work with...

#wrangle the demographics data out of the raw

#temp2 <- dat_age_gender %>% 
  #mutate allows you to change or create variables
 # mutate(unique_id_2 = unique_id * 2)
#we want to change response 

temp5 <- dat_age_gender %>% 
  rename(any_of("male" = "MALE", "Male"))
  rename(any_of("female" = "Female", "FEMALE"))
  rename(any_of("non-binary" = "NON-BINARY", "non binary", "NON BINARY", "Non-Binary", "Non-binary", "Non Binary", "Non binary", "non-Binary", "non Binary", "nonbinary", "NONBINARY"))

temp5 <- dat_age_gender %>%
  distinct(response) 

#For some reason it doesn't work at all
# What I would want to do: 
#   Change the answers from total chaos to either male, female or non-binary, maybe even just male or female
#   then exclude the funny answers (23, yes,...)
#depending on what i would want to do later on with the data i would consider changing the answers to a numeric system like 0 = mal, 1 = female, or 1 = male, 2 = female

#2. Versuch mithilfe eines YT Videos
#https://www.youtube.com/watch?v=224AetNhv3M

install.packages("car")
library(car)

dat_age_gender$gender_rekodiert <- Recode(dat_age_gender$response, 
                                          "male" = "Male";
                                          "female" = "Female")
#doesn't seem to work either, maybe cause it's letters/ words instead of numbers that the guy in the yt video used?

# 3. Try, Chat-GPT second attempt. 
###
# 1. Einheitliche Groß-/Kleinschreibung verwenden
# Du kannst die Groß-/Kleinschreibung einheitlich gestalten, um sicherzustellen, dass alle Werte in derselben Form vorliegen, z. B. alles klein oder alles groß schreiben.
# 
# r
# Code kopieren
# # Beispiel-Daten
# df <- data.frame(Item = c("Apfel", "apfel", "Banane", "banane", "APFEL"))
# 
# # Alles in Kleinbuchstaben umwandeln
# df$Item <- tolower(df$Item)
# 
# # Oder: Alles in Großbuchstaben umwandeln
# # df$Item <- toupper(df$Item)
# 
# print(df)
###

gender_umkodiert <- dat_age_gender(Item = c("Male", "male", "MALE"))
gender_umkodiert$response <- tolower(gender_umkodiert$response)

gender_umkodiert <- dat_age_gender %>%
  distinct(response) 






#to add # to multiple lines: Ctrl + shift + C
#check data type (just an useful fyi)
sapply(dat_age_gender, class)
  
```

# Exclusions / data quality

## AMP

Create an exclusion variable `exclude_amp_performance` based on AMP performance: "exclude" if more than 10% of trials are < 100ms, or "include" if not.

Create an exclusion variable `exclude_amp_completeness` based on the AMP having the right number of trials.

```{r}

#data_amp_performance_criteria <- data_amp_raw 

```

# Self-reports

Create a mean score for each participant of the three self-report items.

```{r}

#data_selfreport_trial_level <- data_selfreport_raw 

```

# Affect Misattribution Procedure

Create an overall AMP bias score. Score each trial as having been evalauted as congruent with the prime or not. eg When trialcode == "prime_positive" & evaluative_response == 1, then record as 1, etc. AMP score is the proportion of congruent responses.

```{r}

#data_amp_score_congruence <- data_amp_raw 

```

# Combine 

Combine data frames together to create one wide-format data frame where each row represents a participant.

Flag all duplicates for exclusion.

```{r}

# data_processed_before_exclusions 

```

# Define master exclusion variable

```{r}

#data_processed <- data_processed_before_exclusions

```

# Write to disk

```{r}

# # in case this dir doesn't exist, create it
# dir.create("../data/processed/")
# 
# # save data to disk in that dir
# write_csv(data_processed, "../data/processed/data_processed.csv")

```

# Session info

```{r}

sessionInfo()

```


